---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dpi = 300
)
```

# multiscales

Multivariate scales for ggplot2, written by Claus O. Wilke


## Installation

This package can be installed from github. It requires the development version of the colorspace package. It also requires ggplot2 3.0.0, which was released on July 3, 2018.
```
install.packages("colorspace", repos = "http://R-Forge.R-project.org")
devtools::install_github("clauswilke/multiscales")
```
This is an experimental package. Use at your own risk. API is not stable. No user support provided.

## Examples

Visualizing both the median house value and its uncertainty for Florida counties:
```{r message = FALSE}
library(ggplot2)
library(multiscales)

colors <- scales::colour_ramp(
  colors = c(red = "#AC202F", purple = "#740280", blue = "#2265A3")
)((0:7)/7)

ggplot(US_polling) + 
  geom_sf(aes(fill = zip(Clinton_lead, moe_normalized)), color = "gray30", size = 0.2) + 
  coord_sf(datum = NA) +
  bivariate_scale("fill",
    pal_vsup(values = colors, max_desat = 0.8, pow_desat = 0.2, max_light = 0.7, pow_light = 1),
    name = c("Clinton lead", "uncertainty"),
    limits = list(c(-40, 40), c(0, 1)),
    breaks = list(c(-40, -20, 0, 20, 40), c(0, 0.25, 0.50, 0.75, 1.)),
    labels = list(waiver(), scales::percent),
    guide = "colourfan"
  ) +
  theme_void() +
  theme(
    legend.key.size = grid::unit(0.8, "cm"),
    legend.title.align = 0.5,
    plot.margin = margin(5.5, 20, 5.5, 5.5)
  )
```

For comparison, the same plot with a univariate color scale:
```{r message = FALSE}
ggplot(US_polling) + 
  geom_sf(aes(fill = Clinton_lead), color = "gray30", size = 0.2) + 
  coord_sf(datum = NA) +
  scale_fill_gradient2(
    low = "#AC202F", mid = "#740280", high = "#2265A3",
    name = c("Clinton lead", "uncertainty"),
    limits = c(-40, 40),
    breaks = c(-40, -20, 0, 20, 40),
    guide = guide_colorbar(
      direction = "horizontal",
      label.position = "bottom",
      title.position = "top",
      barwidth = grid::unit(4.0, "cm")
    )
  ) +
  theme_void() +
  theme(
    legend.title.align = 0.5,
    legend.key.size = grid::unit(0.8, "cm"),
    plot.margin = margin(5.5, 20, 5.5, 5.5)
  )
```
